Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-07-30 paper.tex
Added ROC analysis

\todo{Soudabeh: Different number of factors: type 8, RFNU, 50, 100, 200, 400.}

>>>>

\subsubsection{ROC analysis}

Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
The PreFreesurfer dataset is not included since specificity of RFNTL, 
RFNU, RS and complete rows is undefined at this training ratio (the 
test set only contains positive elements \todo{check matrix with 
Soudabeh to confirm}). The average sensitivity and specificity values 
are reported in Table~\ref{table:roc}. On average, RFNU is the best 
performing method.

\begin{figure*}
\includegraphics[width=\columnwidth]{data/results/roc/roc.pdf}
\includegraphics[width=\columnwidth]{data/results/roc/roc-closeup.pdf}
\caption{Comparison of the sampling methods in the ROC space for the 6 synthetic datasets and Freesurfer. Right: entire dataset. Left: close-up on the top-left part.}
\label{fig:roc}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{ccc}
& Sensitivity & Specificity \\
\hline
Complete Columns & 0.53 & 0.97\\
Complete Rows & 0.43 & 0.89\\
Random Subjects & 0.88 & 0.99\\
RFNU & 0.92 & 0.99 \\
RFNTL & 0.81 & 0.97\\
RFNTS & 0.65 & 0.93 \\
Random Unreal & 1 & 1
\end{tabular}
\caption{Average sensitivity and specificity values for the 6 synthetic datasets and Freesurfer.}
\label{table:roc}
\end{table}

\subsection{Effect of the number of factors}
\todo{Soudabeh: Different number of factors: type 8, RFNU, 50, 100, 200, 400.}
